---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(classdata)
```
# Step 1
```{r}
colnames(ames)
str(ames)
head(ames)
max(ames$`Sale Price`)
```
As a team we saw that there are numeric and categorical variables. Some of the numeric variables are TotalLivingArea (sf), Sale Price, Year Built, Acres, etc. Some of the categorical variables are Fire Place, AC, Multi Sale, etc. The categorical are either Yes or No. We would predict the sale price ranging from 0-3 million. 

#Step 2 
The variable of interest is "Sale Price"

#Step 3
```{r}
library(ggplot2)
salePriceGraph <- ggplot(ames, aes(x=`Sale Price`)) + 
  geom_histogram(binwidth = 500000)

print(salePriceGraph)
```
As a team when exploring the Sale Price variable through the histogram. Most homes look to be between 75k to 150k. There are some outliers where some homes are in the millions but not many at all. 

#Step 4 

